---
title: "Penguins"
author: "Kiran Favre"
date: "2022-08-02"
output: html_document
---

```{r setup, include=FALSE}
knitr::opts_chunk$set(echo = TRUE)
library(tidyverse)
library(palmerpenguins)
```

Examples of printing lines of data from data frame

```{r}
head(penguins)

# or glimpse(penguins)
```


## Scatter plot of body mass versus flipper length

```{r}
#must start with ggplot, tell it what data set to use and which x and y you are interested in, and then tell it the geometry
#now we want to make each type of penguin a certain color by giving geom_point an input

ggplot(data= penguins, aes(x = body_mass_g, y = flipper_length_mm))  + geom_point(aes(color = species), size = 3) + facet_wrap(~island) + theme_minimal() + labs( x = "Body mass (g)", y = "Flipper length (mm)")


```



- aes inputs are specific to changing the VARIABLES within a data set, if you want to make a change to the whole data set then it should be outside the aes function. Make sure if it is referencing a variable, include in aes and if nnot, outside of aes

- here to make a change to practice using git and terminals

